A performance comparison of Dask and Apache Spark for data-intensive neuroimaging pipelines

### 2019-09-26 latex/paper.tex
Modified Introduction

\section{Introduction}
% Context
The recent rise in data sharing and improved data collection strategies
have brought neuroimaging to the Big Data era~\cite{ALFAROALMAGRO:18,
van2014human}. Existing neuroimaging workflow engines, such as
Nipype~\cite{Nipype:11}, are well suited for processing the standard
compute-intensive neuroimaging pipelines, but lack incorporated Big Data
strategies (i.e. in-memory computing, data locality, and lazy-evaluation) to
improve performance of the increasingly prevalent data-intensive pipelines.
As was noted in~\cite{hayot2019performance}, in-memory computing, coupled
with data locality, can bring significant performance improvements to data
intensive neuroimaging pipelines. We extend this work by studying the
differences between two Big Data engines, Dask~\cite{Dask:15} and Apache
Spark~\cite{Spark:16}, for their suitability in the processing of neuroimaging
pipelines. Our goal is to test whether Spark or Dask has a clear
performance advantage to process Big neuroimaging Data.

@@

On Figure~\ref{fig:inc_tt_worker}, we also note that Spark's overhead is
slightly lower than Dask's, particularly when the number of workers
increases. Moreover, Delayed and Futures have a higher overhead than Bag.
However, overhead differences are compensated by an increase in data
transfer time, as a reduced overhead increases the concurrency between data
transfers and the application saturates the 10Gbits/s network bandwidth.

>>>>

\section{Introduction}
% Context
The recent rise in data sharing and improved data collection strategies have brought
neuroimaging to the Big Data era~\cite{ALFAROALMAGRO:18, van2014human}. Existing
neuroimaging workflow engines, such as Nipype~\cite{Nipype:11}, are well suited for
processing the standard compute-intensive neuroimaging pipelines, but lack
incorporated Big Data strategies (i.e. in-memory computing, data locality, and
lazy-evaluation) to improve performance of the increasingly prevalent data-intensive
pipelines. As was noted in~\cite{hayot2019performance}, in-memory computing, coupled
with data locality, can bring significant performance improvements to data intensive
neuroimaging pipelines. We are interested in the impact on performance when
implementing these Big Data strategies in different engines. Our work studies the
differences between two Big Data engines, Dask~\cite{Dask:15} and Apache
Spark~\cite{Spark:16}, for their suitability in the processing of neuroimaging
pipelines. Our goal is to test whether Spark or Dask has a clear performance
advantage to process Big neuroimaging Data.

@@

On Figure~\ref{fig:inc_tt_worker}, we also note that Spark's overhead is
slightly lower than Dask's, particularly when the number of workers
increases. Moreover, Delayed and Futures have a higher overhead than Bag.
However, overhead differences are compensated by an increase in data
transfer time, as a reduced overhead increases the concurrency between data
transfers and the application saturates the disk bandwidth of the shared file system.
